
There are many people that I would like to thank for a rewarding and enjoyable DPhil.

First and foremost, my thanks go to my supervisors Sneha Malde and Neville Harnew. Sneha for her guidance and support throughout the DPhil and teaching me so much about both physics and life. I thank Neville for being there for advice whenever I needed it. I would also like to thank Malcolm John, for his enthusiasm and encouragement throughout my DPhil.

My thanks go to my many fellow Oxford LHCb students throughout the years, for their helpful discussions, office companionship and willingness to answer my many questions. Also, I would also like to thank my friends and colleagues both in Oxford and CERN for the many and varied stimulating, and often downright strange, discussions.

I am very grateful to have had the continued support of my friends and family throughout the last three and a half years. Especially my parents, whose wise words never fail to put things in perspective, and Jacob, who has been there throughout my whole DPhil, making me laugh and keeping me sane. I would also like to thank those people who made the change from Cambridge to Oxford; their friendship and support, as well as the many dinners, pub trips and tea sessions, has made my time in Oxford an extremely happy one.

I would like to extend my gratitude to the Science and Technology Facilities Council (STFC) for providing my funding, as well as Brasenose College; the people, formal dinners and second desserts have helped to make my time at Oxford more enjoyable.